%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

\usepackage{hyperref}

\usepackage{hyperref}
% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo{./examples/profile.png}
\name{Lauren}{Brown}
\position{Software Engineer{\enskip\cdotp\enskip}Electronic Engineer}
\address{18 Auclum Close, Burghfield Common, Reading, RG73DY}

\mobile{(+44)7932784071}
\email{lauren.brown@mailbox.org}
\homepage{https://sigsegv.tech}
\github{IGBC}
% \linkedin{posquit0}
\gitlab{IGBC}
% \stackoverflow{5837486}{lord-nibbler}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Lauren Brown - Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%-------------------------------------------------------------------------------
\cvsection{Skills}
\begin{cvskills}
  \cvskill{Programming}
  {Rust, Python, C, C++, Java, LUA}
  \cvskill{Hardware Engineering}
  {Digital Systems Engineering, Analog Design, PCB Design}
  \cvskill{Project Management}
  {Project Planning, Software Engineering, Systems Administration}
\end{cvskills}

\cvsection{Education}
\begin{cventries}
  \cventry
    {MEng Electronic Engineering (Current Student)} % Degree
    {University of Surrey} % Institution
    {Guildford, England} % Location
    {Oct. 2014 - Aug. 2015; Oct. 2018 - Present} % Date(s)
    {Expected to Graduate in July 2021 with a 2-1 class Master's degree. Bacholors thesis in adding Live Patching to FreeRTOS}
    
  \cventry
    {4 A levels} % Degree
    {Kennet School} % Institution
    {Thatcham, Berkshire, England} % Location
    {Sept. 2012 - Jul. 2014} % Date(s)
    {
      Computing{\enskip\cdotp\enskip}Physics{\enskip\cdotp\enskip}Mathematics{\enskip\cdotp\enskip}Further Mathematics
    }
\end{cventries}

\cvsection{Experience}
\begin{cventries}
  \cventry
    {Head of Hardware Development \& Software Engineer} % Job title
    {Fast Forward Imaging GmbH} % Organization
    {Berlin, Germany} % Location
    {Mar. 2017 - Feb. 2018} % Date(s)
    {\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Technologies: Python{\enskip\cdotp\enskip}Ruby{\enskip\cdotp\enskip}C (Embedded){\enskip\cdotp\enskip}PCB Design{\enskip\cdotp\enskip}Digital Electronics{\enskip\cdotp\enskip}Server Administration}}
        \item {Lead an initiative to augment product with 3D capabilities.}
        \item {Worked with customers to implement custom features on existing products.}
        \item {Responsible for systems administration duties of the company's entire server and cloud infrastructure.}
        \item {Worked in a team, and with manufacturers to produce documentation and solid designs aiding in transitioning to external production.}
        \item {Lead product support team, including remote and in the field debugging of products.}
      \end{cvitems} 
     }

  \cventry
    {Hardware \& Software Developer} % Job title
    {Botspot GmbH} % Organization
    {Berlin, Germany} % Location
    {Nov. 2015 - Mar. 2017} % Date(s)
    {\begin{cvitems} % Description(s) of tasks/responsibilities
         \item {\textbf{Technologies: C, C++{\enskip\cdotp\enskip}LibUSB{\enskip\cdotp\enskip}PCB Design{\enskip\cdotp\enskip}Digital Electronics}}
        \item {Designed Control hardware, software, and networking for new Generation of 3D scanners.}
        \item {Designed camera control software from scratch (C++, LibUSB) to work with proprietary cameras.}
        \item {Provided upgrades to existing Products to improve their reliability and lifespan.}
      \end{cvitems}
    }

  \cventry
    {Industrial Placement (Summer Internship)} % Job title
    {AWE} % Organization
    {Aldermaston, England} % Location
    {Aug. 2015 - Oct. 2015} % Date(s)
    {Electronics Work. Details protected under confidentiality agreements.}   
\end{cventries}

\cvsection{Extra Curricular}
\begin{cventries}
  \cventry
    {Created and Ran a Society at Surrey University's Students Union}
    {Sythesiser and Electronic Music Society}
    {}{}
    {Supporting students in creating DIY musical instruments.}

  \cventry
  {Volenteering in undergraduate labs}
  {Lab PALS scheme}
  {}{}
  {Supporting teaching, by providing assistance to students in regular lab sessions}
  }

  \cventry
    {Open Source Book Scanner - Lead Electronics Engineer.} % Subtitle
    {Libreflip} % Title
    {}{} % Drop left fields
    {Team Project to create an automatic page turning book scanner.}

  \cventry
    {I create open source software in my free time:} % Subtitle
    {Personal Software projects} % Title
    {}{\href{https://github.com/IGBC}{github.com/IGBC}} % Drop left fields
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{https://github.com/IGBC/IDE-Test-Jig}{\textbf{idetestjig}} (C): Building a bit banged IDE interface on an STM32. (For use in an audio recorder.)}
        \item {\href{https://github.com/IGBC/Rustic-Zen}{\textbf{Rustic Zen}} (C++ + Rust): Optimising then Reimplementing an artistic ray tracer first in C++ then Rust.}
        \item {\href{https://github.com/Neotron-Compute}{\textbf{Neotron}} (Rust + KiCAD): Contributing to the development of an open MCU based SBC, with rust firmware.}
        \item {Founding Member of the Rust \href{https://github.com/Rust-Retro}{\textbf{Retro Technologies Working Group (RWG)}}, an unoffical working group with the goal to bring rust to as much outdated hardware as possible.}
        \item {\href{https://gitlab.com/IGBC/SegNAND}{\textbf{SegNAND}} (Electronics) \& \href{https://github.com/IGBC/audio-af}{\textbf{Audio-AF}} (Rust) (Just Started): My experiments with electronic music, trying to make interesting sounding instruments.}
      \end{cvitems} 
     }

  \cventry
    {Ask For "SEGFAULT"} % Subtitle
    {Active Chaos Computer Club (CCC) Community Member} % Title
    {}{} % Drop left fields
    {Until returning to university I was a regular contributor to Berlin hacker-spaces.}

\end{cventries}

\cvsection{Other Skills}
\begin{cventries}
  \cventry
   {} % Subtitle
   {Holds full UK Driving licence} % Title
   {}{} % Drop left fields
   {}

  \cventry
   {} % Subtitle
   {Speaks native English and limited German} % Title
   {}{} % Drop left fields
   {}

   \cventry
   {} % Subtitle
   {Has been "Daily Driving" Linux for almost 7 years} % Title
   {}{} % Drop left fields
   {}
\end{cventries}   


\end{document}
